---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(sf)
library(raster)
library(here)
library(stars)
library(RColorBrewer)
library(ggpattern)
library(ggmap)
library(leaflet)
library(leaflet.providers)
library(leaflet.esri)
library(ggpubr)
library(cowplot)
library(viridis)

rf <- colorRampPalette(rev(brewer.pal(11,'Spectral')))
r <- rf(32)
```

```{r}
#predictive
ras_res <- raster(here("methods", "penn_shiny_app", "prerender_PA_app", "m0r10.tif")) 
ras_mig <- raster(here("methods", "penn_shiny_app", "prerender_PA_app", "m10r0.tif")) 

#landscape
lsm_10km_agri <- raster(here("methods", "Penn_migration_model", "lsm_10km", "lsm_agri_90m_10km_5070.tif")) 
lsm_10km_dev <- raster(here("methods", "Penn_migration_model", "lsm_10km", "lsm_dev_90m_10km_5070.tif")) 

#level iii ecoregions
ras_ecoregion <- here("methods", "Penn_migration_model", "additional_covariates", "level_iii_ecoregions_pa.tif") %>% raster()

#terrain
drainage_30m <- here("methods", "Penn_migration_model", "additional_covariates", "soil_drainage_5070.tif") %>% raster() 
```

Standardizing by quantile
```{r}
quantiles <- raster::quantile(ras_res, 1:100/100)
intervals <- findInterval(getValues(ras_res), quantiles)
ras_res <- setValues(ras_res, intervals)

quantiles <- raster::quantile(ras_mig, 1:100/100)
intervals <- findInterval(getValues(ras_mig), quantiles)
ras_mig <- setValues(ras_mig, intervals)
```


Generate sample points
```{r}
#landcover: set background values to NA
forest_30m <- here("methods", "Penn_migration_model", "additional_covariates", "nlcd2016_forestpatches.tif") %>% raster() 
forest_30m[forest_30m == 128] <- NA

sample_points <- enmSdmX::sampleRast(x = projectRaster(forest_30m, crs = crs("+init=epsg:4326")), n = 10000, replace = TRUE, prob = FALSE) %>%
  as.data.frame()

coordinates(sample_points) <- ~ x + y

proj4string(sample_points) <- CRS("+init=epsg:4326")

sample_points <- st_as_sf(sample_points)

sample_points %>%
  st_transform(st_crs(5070)) ->
  sample_points

sample_points <- as_Spatial(sample_points)
```

Extract values at these points
```{r}
values_res <- ras_res %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)

values_mig <- ras_mig %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)

values_ecoregion <- ras_ecoregion %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)

values_10km_agri <- lsm_10km_agri %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)

values_10km_dev <- lsm_10km_dev %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)

values_drainage <- drainage_30m %>% 
  projectRaster(from = ., crs = "+init=epsg:5070") %>%
  raster::extract(x = ., y = sample_points)
```

```{r}
point_values <- sample_points %>%
  st_as_sf() %>%
  mutate(
    res = values_res,
    mig = values_mig,
    ecoregion = values_ecoregion,
    agri10km = values_10km_agri,
    dev10km = values_10km_dev,
    drainage = values_drainage
  )
```

```{r}
point_values -> point_values_sampled
```

```{r}
point_values_sampled %>%
  pivot_longer(cols = c(mig, res), names_to = "season") ->
  point_values_longer
```

Relationships with variables for each season

Agri 10km
```{r}
agri_10km_plot <- point_values_longer %>%
  mutate(season = recode(season, "mig" = "Migratory", "res" = "Breeding" )) %>%
  ggplot(aes(x = agri10km, y = value)) +
  geom_hex() +
  #geom_point() +
  theme_bw() +
  facet_wrap(~season)  +
  ylab("Habitat suitability") +
  xlab("Percent agricultural (10 km)") +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = .25)) +
  scale_fill_gradientn(colours=rf(405), limits = c(1,405), trans = "log", labels = round) +
  labs(fill="Count") + 
  theme(legend.position = "none")

agri_10km_plot

ggsave(plot = agri_10km_plot,
       filename = here("figures_results","covariate_graphs_figure", "agri_10km_4_19_26.png"), height = 4, width = 7, dpi = 600)
```

dev 10km (good one to show tolerance for developed landscapes among migratory birds)
```{r}
dev_10km_plot <- point_values_longer %>%
  mutate(season = recode(season, "mig" = "Migratory", "res" = "Breeding" )) %>%
  ggplot(aes(x = dev10km, y = value)) +
  geom_hex() +
  #geom_point() +
  theme_bw() +
  facet_wrap(~season) +
  ylab("Habitat suitability") +
  xlab("Percent developed (10 km)") +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_gradientn(colours=rf(405), limits = c(1,405), trans = "log", labels = round) + 
  labs(fill="Count") + 
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank())

dev_10km_plot

ggsave(plot = agri_10km_plot,
       filename = here("figures_results","covariate_graphs_figure", "dev_10km_4_19_26.png"), height = 4, width = 7, dpi = 600)
```

drainage
```{r}
drainage_tbl <- point_values_longer %>%
  mutate(season = recode(season, "mig" = "Migratory", "res" = "Breeding" ),
         drainage = round(drainage)) %>%  
         # drainage = as.factor(recode_values(round(drainage), 
         #                   0 ~ "Excessively drained",
         #                   1 ~ "S. excessively drained",
         #                   2 ~ "Well drained",
         #                   3 ~ "M. well drained",
         #                   4 ~ "S. poorly drained",
         #                   5 ~ "Poorly drained",
         #                   6 ~ "V. poorly drained"))) %>% 
  filter(!is.na(drainage))

# drainage_tbl$drainage <- factor(drainage_tbl$drainage, levels = c("Excessively drained", "S. excessively drained", "Well drained", "M. well drained", "S. poorly drained", "Poorly drained", "V. poorly drained"), ordered = TRUE)

drainage_plot <- drainage_tbl %>% 
  ggplot(aes(x = drainage, y = value)) +
  geom_hex() +
  #geom_point() +
  theme_bw() +
  facet_wrap(~season) +
  ylab("Habitat suitability") +
  xlab("Soil drainage class") +
  #scale_x_continuous(labels = scales::percent) +
  scale_fill_gradientn(colours=rf(405), limits = c(1,405), trans = "log", labels = round) + 
  labs(fill="Count") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank())

drainage_plot

 ggsave(plot = drainage_plot,
       filename = here("figures_results","covariate_graphs_figure", "drainage_4_19_26.png"), height = 4, width = 7, dpi = 600)
```


```{r fig.height=4, fig.width=10}
ggarrange(agri_10km_plot, dev_10km_plot, drainage_plot, ncol = 3, nrow = 1, widths = c(3.1,3,3))
ggsave(here("figures_results","covariate_graphs_figure", "covariate_comparison.png"), height = 4, width = 10, dpi = 600, units = "in")
```
1) woodcock are much more tolerant of high % agri during migration
2) woodcock use developed areas less during breeding and more during migration
3) woodcock use poorly-drained areas similarly during both seasons, but this effect is a more important predictor during migration

