---
title: "R Notebook"
output: html_notebook
---

Run these after the comparative_distribution_models script

Removing: High res landscape layers
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_1k_5k_30m_5070 + ai_1k_5k_30m_5070 + cohesion_1k_5k_30m_5070 + ed_1k_5k_30m_5070 + factor(layer.1) + DEM_PA_30m + DEM_PA_30slope + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6436686
```

Removing: Low res landscape layers
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_200m_1k_30m_5070 + ai_200m_1k_30m_5070 + cohesion_200m_1k_30m_5070 + ed_200m_1k_30m_5070 + factor(layer.1) + DEM_PA_30m + DEM_PA_30slope + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6658571
```

Removing: All landscape layers
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="factor(layer.1) + DEM_PA_30m + DEM_PA_30slope + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6351174
```

Removing: forest_30m
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_200m_1k_30m_5070 + ai_200m_1k_30m_5070 + cohesion_200m_1k_30m_5070 + ed_200m_1k_30m_5070 + pland_1k_5k_30m_5070 + ai_1k_5k_30m_5070 + cohesion_1k_5k_30m_5070 + ed_1k_5k_30m_5070 +  DEM_PA_30m + DEM_PA_30slope + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6646205
```

Removing: elevation
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_200m_1k_30m_5070 + ai_200m_1k_30m_5070 + cohesion_200m_1k_30m_5070 + ed_200m_1k_30m_5070 + pland_1k_5k_30m_5070 + ai_1k_5k_30m_5070 + cohesion_1k_5k_30m_5070 + ed_1k_5k_30m_5070 + factor(layer.1) + DEM_PA_30slope + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6430979
```

Remove: slope
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_200m_1k_30m_5070 + ai_200m_1k_30m_5070 + cohesion_200m_1k_30m_5070 + ed_200m_1k_30m_5070 + pland_1k_5k_30m_5070 + ai_1k_5k_30m_5070 + cohesion_1k_5k_30m_5070 + ed_1k_5k_30m_5070 + factor(layer.1) + DEM_PA_30m + layer.2 + DEM_PA_30m_twi", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6687257
```

Remove: soil drainage and topographic wetness index
```{r}
#Creating a vector of routes that can be used as a random effect and embedding them into a modified swd
swd_modified <- swd
swd_modified@data$route <- bind_rows(st_as_sf(avail), st_as_sf(used)) %>%
  cbind(., st_coordinates(.)) %>% 
  st_drop_geometry %>%
  left_join(swd@coords, .) %>%
  pull(Route)

#iterate through folds 
folds <- .convert_folds(swd_folds_custom, swd_modified)
k <- ncol(folds[[1]])

models <- vector("list", length = k)

#train models
for (j in 1:k) {
  print(paste("Running model: ",j))
  train <- .subset_swd(swd_modified, folds$train[, j])
  models[[j]] <- MixRFb(Y = train$pa, x ="pland_200m_1k_30m_5070 + ai_200m_1k_30m_5070 + cohesion_200m_1k_30m_5070 + ed_200m_1k_30m_5070 + pland_1k_5k_30m_5070 + ai_1k_5k_30m_5070 + cohesion_1k_5k_30m_5070 + ed_1k_5k_30m_5070 + factor(layer.1) + DEM_PA_30m + DEM_PA_30slope", random='(1|route)', data = train$data, initialRandomEffects=0, ErrorTolerance=1, MaxIterations=200, ErrorTolerance0=0.3, MaxIterations0=5, verbose=T)
  }

#test models

aucs <- vector("list", length = k)

for (j in 1:10){ #should be 1 through 10, there's a bug with 10
  test <- .subset_swd(swd_modified, folds$test[, j]) #
  pred1 <- predict.MixRF(models[[j]], test$data, EstimateRE=FALSE)
  n_p <- sum(test$pa == 1)
  n_a <- sum(test$pa == 0)
  Rp <- sum(rank(pred1)[1:n_p]) # Sum of rank of positive cases
  Up <- Rp - (n_p * (n_p + 1) / 2)  # U test for positive cases
  aucs[[j]] <- Up / (n_p * n_a)
} 
aucs %>% 
  as.numeric() %>% 
  mean() #0.6617948
```

Preparing a better jacknifing figure showing the AUC penalty associated with single variable and suite model exclusion
Based on the all inclusive RF w/ random effects (reference 0.6529721)

Variable importance is measured as the reduction in AUC when the variable/suite is removed from the full model. 

Variables with positive values improve our predictive capacity, and variables with negative values detract from it 

Asterisk indicates a suite of highly correlated variables

"All Landscape" 0.0178547
"Elevation" 0.0098742
"High Res Landscape" 0.0093035
"Soil Moisture" -0.0088227
"Forest" -0.0116484
"Low Res Landscape" -0.012885
"Slope" -0.0157536


```{r}
jacknife_df <- tibble(`Excluded Variable/Suite` = as_factor(c("Slope", "Low Res\n Landscape", "Forest", "Soil Moisture", "High Res\n Landscape", "Elevation", "All Landscape")), `Variable Importance` = c(-0.0157536, -0.012885, -0.0116484, -0.0088227, 0.0093035, 0.0098742, 0.0178547))

jacknife_df %>%
  mutate(pos_neg = if_else(`Variable Importance` > 0, 'a', 'b')) %>%
ggplot(mapping = aes(x = `Excluded Variable/Suite`, y = `Variable Importance`, fill = pos_neg)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = c("#06A4C5", "#C52706")) +
  theme(legend.position = "none")# +
  #ylim(-0.03, 0.05)

ggsave("variable_importance_4_18_21.jpg")
```

